---
title: "FCC Data"
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#| label:   "Set environment"

### set environment
library("tidyverse")
library("knitr")

FD_DOC = "../"
FD_TAB = file.path(FD_DOC, "table")
FD_FIG = file.path(FD_DOC, "figure")
```

## WHG-STARR-seq (WSTARR)

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#| label:   "FCC Metadata (WSTARR)"
#| tbl-cap: "FCC Metadata (WSTARR)"

### set directory
txt_fdiry = file.path(FD_DOC, "table")
txt_fname = "metadata.wstarr.tsv"
txt_fpath = file.path(txt_fdiry, txt_fname)

### read table
dat = read_tsv(txt_fpath)

### arrange table
dat = dat %>% dplyr::select("FName", "Group", "Sample")
colnames(dat) = c("File Name", "Group", "Sample")

### show table
kable(dat)
```

## ATAC-STARR-seq (ASTARR)

## Tiling MPRA (TMPRA)

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#| label:   "FCC Region Screened (TMPRA)"
#| tbl-cap: "FCC Region Screened (Tiling-MPRA)"

### set directory
txt_fdiry = file.path(FD_DOC, "table")
txt_fname = "region_screened.tmpra.tsv"
txt_fpath = file.path(txt_fdiry, txt_fname)

### read table
dat = read_tsv(txt_fpath)

### show table
kable(dat)
```

## Lenti-MPRA (LMPRA)

![LMPRA Log2FC (Features)](../figure/02_prepare/fig.fcc_assay.LMPRA.hist.Log2fc.split.svg)

::: {#fig-LMPRA-prepare-hist layout-ncol=3}

![LMPRA Log2FC (Total)](../figure/02_prepare/fig.fcc_assay.LMPRA.hist.Log2fc.total.svg)

![LMPRA Log2FC (Neg. Ctrl)](../figure/02_prepare/fig.fcc_assay.LMPRA.hist.Log2fc.neg_ctrl_shuffled.svg)

![LMPRA Log2FC and z score](../figure/02_prepare/fig.fcc_assay.LMPRA.hist.Log2fc.zscore.svg){width=120%}

Distribution of LMPRA Log2 fold change
:::

## CRISPRi-HCR FlowFISH (CRISPRi-HCRFF)

## CRISPRi Growth screen (CRISPRi-Growth)

## CRISPR E2G benchmark data (CRISPR-E2G)
```
EPCrisprBenchmark_ensemble_data_GRCh38.tsv
Biosample: K562
Reference
Ulirsch2016
Gasperini et al., 2019
Wakabayashi2016
Schraivogel et al., 2020
Klann2017
Thakore2015
Xie2017
Fulco2019
Qi2018
Huang2018
Xu2015
Fulco2016

#EP links = 10,412
#Regulated     =   487 (~4.7% of total)
#Not Regulated = 9,924
```

