---
title: "FCC Data"
---

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#| label:   "Set environment"

### set folder
FD_REPO = "/mount/repo"
FD_PRJ = file.path(FD_REPO, "Proj_ENCODE_FCC")
FD_EXE = file.path(FD_PRJ,  "scripts")

### set environment
txt_fdiry = FD_EXE
txt_fname = "config_project_site.R"
txt_fpath = file.path(txt_fdiry, txt_fname)
source(txt_fpath)
```

## WHG-STARR-seq (WSTARR)

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#| label:   "FCC Metadata (WSTARR)"
#| tbl-cap: "FCC Metadata (WSTARR)"

### set directory
txt_fdiry = file.path(FD_RES, "assay_fcc", "STARR_WHG_K562_Reddy_A001", "fragment_counts", "summary")
txt_fname = "metadata.tsv"
txt_fpath = file.path(txt_fdiry, txt_fname)

### read table
dat = read_tsv(txt_fpath)

### arrange table
dat = dat %>% dplyr::select("FName", "Group", "Sample")
colnames(dat) = c("File Name", "Group", "Sample")

### show table
kable(dat)
```

## ATAC-STARR-seq (ASTARR)

## Tiling MPRA (TMPRA)

```{r, echo=FALSE, message=FALSE, warning=FALSE}
#| label:   "FCC Region Screened (TMPRA)"
#| tbl-cap: "FCC Region Screened (Tiling-MPRA)"

### set directory
txt_fdiry = file.path(FD_RES, "region", "fcc_screened")
txt_fname = "region_screened.tmpra.tsv"
txt_fpath = file.path(txt_fdiry, txt_fname)

### read table
dat = read_tsv(txt_fpath)

### show table
kable(dat)
```

## Lenti-MPRA (LMPRA)

![LMPRA Log2FC (Features)](../figure/02_prepare/fig.fcc_assay.LMPRA.hist.Log2fc.split.svg)

::: {#fig-LMPRA-prepare-hist layout-ncol=3}

![LMPRA Log2FC (Total)](../figure/02_prepare/fig.fcc_assay.LMPRA.hist.Log2fc.total.svg)

![LMPRA Log2FC (Neg. Ctrl)](../figure/02_prepare/fig.fcc_assay.LMPRA.hist.Log2fc.neg_ctrl_shuffled.svg)

![LMPRA Log2FC and z score](../figure/02_prepare/fig.fcc_assay.LMPRA.hist.Log2fc.zscore.svg){width=120%}

Distribution of LMPRA Log2 fold change
:::

## CRISPRi-HCR FlowFISH (CRISPRi-HCRFF)

## CRISPRi Growth screen (CRISPRi-Growth)

## CRISPR E2G benchmark data (CRISPR-E2G)

